ZCB Pricing

### 2018-10-18 ZCB Pricing .Rmd
gummy worm

for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()
  AN[i]=Antithetic_variates()
  MM[i]=Moment_Matching()
  CV[i]=Control_Variates_estimate()
}

var(CR) # variance of crude monte carlo
var(AN) # variance of antithetic variates
var(MM) # variance of moment matching
var(CV) # variance of control variates

>>>>

for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()

for (i in 1:100){
  AN[i]=Antithetic_variates()

for (i in 1:100){
  MM[i]=Moment_Matching()

for (i in 1:100){
  CV[i]=Control_Variates_estimate()
}

VarCR=var(CR) # variance of crude monte carlo
VarAN=var(AN) # variance of antithetic variates
VarMM=var(MM) # variance of moment matching
varCV=var(CV) # variance of control variates
